---
title: "Exam3Markdown"
author: "Evan Shimek"
date: "7/8/2021"
output: word_document
---

```{r}
#1. clear environment
rm(list=ls(all=TRUE))


#2. download WDI data on female labor force participation
library(WDI)

female_lfp = WDI(country = "all",
                 indicator =c("SL.TLF.CACT.FE.NE.ZS"),
                 start = 2010, end = 2015, extra = FALSE, cache = NULL)


#3. rename the female labor force participation variable flfp
library(dplyr)

female_lfp = rename(female_lfp, flfp = SL.TLF.CACT.FE.NE.ZS)


#4. collapse by mean flfp by country

collapsed_flfp = female_lfp %>%
  group_by(country, iso2c) %>%
  summarize(flfp = mean(flfp, na.rm=TRUE))


#5. show which countries have average female force participation rates 
#for the 2010-2015 period that are less than 15%

collapsed_flfp$flfp = as.numeric(collapsed_flfp$flfp)

low_participation_countries = collapsed_flfp %>%
  filter(flfp < 15)

print(low_participation_countries)


#6. map collapsed_flfp onto a world map, using viridis color scheme
library(sf)
library(rnaturalearth)
library(rnaturalearthhires)
library(ggplot2)
library(viridis)

world <-ne_countries(scale = "large", returnclass = "sf")

world = rename(world, iso2c = iso_a2)

merged_data = left_join(world, collapsed_flfp, by="iso2c")


collapsed_flfp_map = ggplot() +
  geom_sf(data = world) +                                             
  geom_sf(data = merged_data, aes(fill=`flfp`)) +                      
  scale_fill_viridis(option = "viridis") +                                
  ggtitle("World Female Labor Participation, in Percent") +      
  theme(plot.title = element_text(hjust = 0.5)) +                                        
  theme_void()  

print(collapsed_flfp_map)
```

7. Based on the map, which area of the world has, perhaps surprisingly, a cluster of yellow-colored average female labor force participation rate states, indicating the highest on the scale? 

**A:** Based on the map, a few nations in Southeast Africa seem to have higher-than-average female labor force participation (nearly at the top of the scale).

```{r}
# 8. show the same cluster of states referenced in the previous question 
library(data.table)

africa = ne_countries(continent = 'Africa',
                      scale = "large",
                      returnclass = "sf")

setnames(merged_data, "sovereignt", "country")


africa_only_data <-subset(merged_data, country=="United Republic of Tanzania"|
                 country=="Democratic Republic of the Congo"|country=="Angola"|
                 country=="Mozambique"|country=="Malawi"|country=="Zambia"|
                 country=="Madagascar"|country=="Zimbabwe"|country=="Eswatini"|
                 country=="Namibia"|country=="Botswana"| country=="South Africa"|
                   country=="Republic of the Congo")


africa_flfp_map = ggplot() +
  geom_sf(data = africa) +                                             
  geom_sf(data = africa_only_data, aes(fill=`flfp`)) +                      
  scale_fill_viridis(option = "viridis") +                                
  ggtitle("Female Labor Participation in Africa, in Percent") +      
  theme(plot.title = element_text(hjust = 0.5)) +                                        
  theme_void()  

print(africa_flfp_map)
```

9. In a Shiny app, what are the three main components and their subcomponents?

**A:** A shiny app is comprised of three main components: a UI, a server, and code to execute the shinyapp. The UI requires a style of input and output to be specified, while the server requires the specification of the back-end code that actually transforms the input to the output.  

```{r}
#10. Pull Pdf from Mike's webpage
library(pdftools)
mytext = pdf_text(pdf = "https://pdf.usaid.gov/pdf_docs/PA00TNMJ.pdf")


#11. Convert pdf to data frame
armeniatext = as.data.frame(mytext, stringsAsFactors=FALSE)


#12. Tokenize by word, removing stop words
library(tidytext)
library(stringr)
library(tidyr)

armeniatext = armeniatext %>%
  unnest_tokens(word, mytext)

data("stop_words")
armeniatext = armeniatext %>%
  anti_join(stop_words)

#13. Figure out the top 5 most used words
most_used = armeniatext %>%
  count(word, sort=T)

print(most_used[1:10,])


#14. Load the billboard Hot 100 webpage
library(rvest)

hot100exam = rvest::read_html("https://www.billboard.com/charts/hot-100")


#15. Identify all nodes using rvest
body_nodes = hot100exam %>%
  rvest::html_node("body") %>%
  rvest::html_children()


#16. Pull data on Rank, Artist, Title, and Last Week
rank = hot100exam %>%
  rvest::html_nodes('body') %>%
  xml2::xml_find_all("//span[contains(@class,                
                     'chart-element__rank__number')]") %>%
  rvest::html_text()

artist <-hot100exam %>%
  rvest::html_nodes('body') %>%
  xml2::xml_find_all("//span[contains(@class,
                     'chart-element__information__artist')]") %>%
  rvest::html_text()

title <-hot100exam %>% 
  rvest::html_nodes('body') %>%
  xml2::xml_find_all("//span[contains(@class,
                     'chart-element__information__song')]") %>%
  rvest::html_text()

last_week <-hot100exam %>% 
  rvest::html_nodes('body') %>%
  xml2::xml_find_all("//span[contains(@class,
                     'chart-element__meta text--center color--secondary text--last')]") %>%
  rvest::html_text()

#16b Save as dataframe, .dta file
chart_df = data.frame(rank, artist, title, last_week)
library(rio)
export(chart_df, "hot100examchart.dta")

```
 17. What is the link to your GitHub repository?
 
 **A:** https://github.com/eshimek/Exam3
